Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-17 Documentation/manuscript.tex
Manuscript edits.
Manuscript table edits

\journalname{Sankhya B}

\usepackage{Sweave}
\begin{document}
\input{manuscript-concordance}

@@

@@

\begin{Schunk}
\begin{Soutput}
% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Wed May 16 17:31:14 2018
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
1 & 2 & 3 & 4 \\ 
  \hline
 &  &  & 7 \\ 
   &  &  & 6 \\ 
   &  &  & 5 \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   \hline
\end{tabular}
\end{table}
\end{Soutput}
\begin{Soutput}
% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Wed May 16 17:31:14 2018
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
1 & 2 & 3 & 4 \\ 
  \hline
 &  &  & 10 \\ 
   &  &  & 9 \\ 
   &  &  & 8 \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   &  &  &  \\ 
   \hline
\end{tabular}
\end{table}
\end{Soutput}
\end{Schunk}

>>>>

\journalname{Sankhya B}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/misslow-1} \caption[Low missingness]{Low missingness}\label{fig:misslow}
\end{figure}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{tabular}{l|l|l|r|r|r|r|r|r}
\hline
Design & Missingness & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
\hline
 &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
\cline{3-9}
 &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
\cline{3-9}
 &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
\cline{3-9}
 &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
\cline{1-9}
 &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
\cline{3-9}
 &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
\cline{3-9}
 &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
\cline{2-9}
 &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
\cline{3-9}
 &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
\cline{1-9}
 &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
\cline{3-9}
 &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
\cline{3-9}
 &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
\cline{3-9}
 &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
\cline{2-9}
 &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
\cline{3-9}
 &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
\cline{3-9}
 &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
\hline
\end{tabular}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in column\_spec(1, width = "{}30em"{}): argument "{}column"{} is missing, with no default}}\begin{verbatim}
## % latex table generated in R 3.4.1 by xtable 1.8-2 package
## % Thu May 17 15:47:48 2018
## \begin{table}[ht]
## \centering
## \begin{tabular}{lllrrrrrr}
##   \hline
## "" & "" & "" & Coverage & Bias & MSE & FMI & CI Length & Pct Bias \\ 
##   \hline
##  &  &  & 0.968 & -0.023 & 0.120 & 0.018 & 1.414 & 0.498 \\ 
##    &  &  & 0.973 & 0.604 & 0.669 & 0.271 & 4.812 & 429.053 \\ 
##    &  &  & 0.955 & 0.010 & 0.048 & 0.003 & 0.827 & 3.263 \\ 
##    &  &  & 0.945 & -0.000 & 0.000 & 0.004 & 0.039 & -2.671 \\ 
##    &  &  & 0.972 & -0.048 & 0.128 & 0.059 & 1.506 & 1.060 \\ 
##    &  &  & 0.988 & 0.724 & 0.898 & 0.499 & 5.933 & 513.940 \\ 
##    &  &  & 0.958 & 0.025 & 0.047 & 0.013 & 0.834 & 7.927 \\ 
##    &  &  & 0.938 & -0.000 & 0.000 & 0.017 & 0.039 & -2.867 \\ 
##    &  &  & 0.984 & -0.178 & 0.370 & 0.132 & 2.050 & 3.882 \\ 
##    &  &  & 0.955 & 0.997 & 1.573 & 0.610 & 6.822 & 708.287 \\ 
##    &  &  & 0.965 & 0.044 & 0.060 & 0.036 & 0.966 & 13.650 \\ 
##    &  &  & 0.955 & -0.000 & 0.000 & 0.060 & 0.048 & -0.787 \\ 
##    &  &  & 0.966 & -0.019 & 0.119 & 0.011 & 1.401 & 0.415 \\ 
##    &  &  & 0.966 & 0.603 & 0.638 & 0.239 & 4.616 & 428.601 \\ 
##    &  &  & 0.956 & 0.014 & 0.048 & 0.002 & 0.827 & 4.254 \\ 
##    &  &  & 0.944 & -0.000 & 0.000 & 0.003 & 0.039 & -3.004 \\ 
##    &  &  & 0.978 & -0.045 & 0.124 & 0.053 & 1.493 & 0.988 \\ 
##    &  &  & 0.974 & 0.728 & 0.879 & 0.504 & 5.976 & 517.389 \\ 
##    &  &  & 0.954 & 0.024 & 0.051 & 0.011 & 0.838 & 7.437 \\ 
##    &  &  & 0.946 & -0.001 & 0.000 & 0.018 & 0.039 & -4.550 \\ 
##    &  &  & 0.984 & -0.117 & 0.196 & 0.112 & 1.759 & 2.557 \\ 
##    &  &  & 0.968 & 0.876 & 1.305 & 0.650 & 6.913 & 622.327 \\ 
##    &  &  & 0.963 & 0.026 & 0.051 & 0.034 & 0.892 & 8.265 \\ 
##    &  &  & 0.949 & -0.001 & 0.000 & 0.055 & 0.043 & -5.340 \\ 
##    &  &  & 0.968 & -0.057 & 0.127 & 0.038 & 1.454 & 1.249 \\ 
##    &  &  & 0.974 & 0.853 & 1.003 & 0.510 & 5.629 & 606.148 \\ 
##    &  &  & 0.959 & 0.006 & 0.046 & 0.006 & 0.831 & 1.804 \\ 
##    &  &  & 0.945 & -0.000 & 0.000 & 0.011 & 0.039 & -3.051 \\ 
##    &  &  & 0.979 & -0.182 & 0.166 & 0.183 & 1.813 & 3.981 \\ 
##    &  &  & 0.967 & 0.979 & 1.325 & 0.782 & 6.758 & 695.352 \\ 
##    &  &  & 0.956 & 0.020 & 0.050 & 0.037 & 0.871 & 6.425 \\ 
##    &  &  & 0.955 & -0.001 & 0.000 & 0.068 & 0.042 & -4.466 \\ 
##    &  &  & 0.987 & -0.403 & 0.345 & 0.440 & 2.789 & 8.803 \\ 
##    &  &  & 0.951 & 1.050 & 1.504 & 0.887 & 7.357 & 745.735 \\ 
##    &  &  & 0.973 & 0.019 & 0.050 & 0.099 & 0.960 & 5.848 \\ 
##    &  &  & 0.975 & -0.003 & 0.000 & 0.200 & 0.052 & -18.904 \\ 
##    \hline
## \end{tabular}
## \end{table}
\end{verbatim}
\end{kframe}
\end{knitrout}
